---
title: "#####"
output:
  html_document:
    df_print: paged
---

---
title: "####"
output:
  html_document:
    df_print: paged
---

### 1.  Data Preparation (20pts)
- Create an R Notebook using RStudion and load the "${\tt Profit by Product.xlsx}$" data file. This table contains bank revenue, cost, and profit data organized by time, distribution channel, product, and customer.

     - Randomly select a subset of 2000 observations from the data file using the R dplyr "${\tt sample\_n}$" command. 
     
     - Create R-friendly variable names using the "${\tt clean\_names}$" funtion found in the "${\tt janitor}$" package.
     
     - Create a new variable "${\tt log\_rev}$" by taking the log of "${\tt revenue}$".
```{r}
library(tidyverse)
library(readxl)
library(janitor)

product_profit <- read_excel("Profit by Product.xlsx")
sample_set <- sample_n(product_profit, 2000)

sample_set <- sample_set %>%
  clean_names()

sample_set <- mutate(sample_set, log_rev = log(revenue))
sample_set
```
### 2.  Numeric Description (30pts) 
-  For variables ${\tt revenue}$, "${\tt profit}$" and ``${\tt product\_cost}$'' describe each variable by finding:
   -  Mean
   -  Mode(s)
   -  Variance
   -  Sample Standard Deviation
   -  5 Number Summary
```{r}
mode_calc <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

sample_set %>%
  summarise(sum = sum(revenue), mode = mode_calc(revenue), var = var(revenue), sd = sd(revenue)) 

sample_set %>%
summarise(sum = sum(profit), mode = mode_calc(profit), var = var(profit), sd = sd(profit))

sample_set %>%
summarise(sum = sum(product_cost), mode = mode_calc(product_cost), var = var(product_cost), sd = sd(product_cost))

summary(sample_set$revenue)
summary(sample_set$product_cost)
summary(sample_set$profit)
```
	             

### 3.  Visualizing the data (50pts)
-  Draw a histrogram for "${\tt customer\_service\_cost}$" and describe the plot.
&nbsp; &nbsp; The plot indicates that customer service cost is generally very low with about a count of 500 at or near zero. The vast majority of the sample is at or below $25. Additional breakdowns by quarter and product line did not show any different conclusions. 
```{r}
ggplot(sample_set, aes(x = customer_service_cost)) +
   geom_histogram(bins=10)

ggplot(sample_set, aes(x = customer_service_cost)) +
   geom_histogram(bins=25) +
   scale_x_continuous(limits = c(0,100))

ggplot(sample_set, aes(x = customer_service_cost)) +
   geom_histogram(bins=10) + 
   facet_wrap(~ quarter)

ggplot(sample_set, aes(x = customer_service_cost)) +
   geom_histogram(bins=10) + 
   facet_wrap(~ product_line)
```
-  Create a scatter plot of "${\tt revenue}$" vs. "${\tt profit}$". What relationship, if any, do you see?
&nbsp; &nbsp; The plot indicates a non-linear relationship between revenue and profit. The direction is negative for negative profit values and positive for positive profit values. The points are largely bunched closely together indicating a fairly strong relationship. 
```{r}
ggplot(sample_set, aes(x = profit, y = revenue)) +
   geom_point(alpha=0.5)
```
- Create box-whisker plots of "${\tt log\_rev}$" by "${\tt quarter}$". Describe the relationships of ${\tt log\_rev}$ within and between quarters.

&nbsp; &nbsp; Log_rev appears to rise Q/Q. The 25th percentile, mean and 75% percentile all rose Q/Q. The letter value boxplot also helps to show this as well. Q3 saw fewer quantiles overall with log_rev skewing higher. This could maybe be due to something like seasonal factors. For further study, I would investigate reason why log_rev (revenue) skews upward closer to the end of the year.
```{r}
ggplot(sample_set, aes(x = quarter, y = log_rev)) +
  geom_boxplot()

library(lvplot)
ggplot(sample_set, aes(x = quarter, y = log_rev)) +
  geom_lv()
```

